\documentclass{article}
\usepackage[a4paper, total={7in, 10in}]{geometry}

\usepackage{lipsum}

\usepackage{lineno}

% \usepackage{float}
% \usepackage[]{graphicx}
% \graphicspath{{Images/}}
% \usepackage{hyperref}
% \usepackage{subfiles}

% \usepackage{biblatex}
% \bibliography{ref.bib}
% \addbibresource{ref.bib}

% \usepackage{booktabs}
% \usepackage{multicol}

% \usepackage{tabularx}

\setlength\parindent{0pt}

% remove section numbering
% \setcounter{secnumdepth}{0}

\begin{document}
\linenumbers

\pagenumbering{arabic}


\title{Constitution of the Imam Mahdi Youth (IMY)}
\author{Members of the Imam Mahdi Youth}
\date{\today}
\maketitle

\section{IMY}
The Imam Mahdi Youth Group (IMY) is a collective of various young people of the Imam Mahdi Islamic Centre in Markham Ontario.
This group numbers around 30-50 active members at any time, and has had a rich history of events.
The group provides programming to build a community to foster a deeper connection to God and Islam.
This simple collective of members strives to foster a sense of \textbf{belonging}, and \textbf{ownership} to the Mosque and Islam.
It practices virtues that all Muslims and humans shall practice especially in the context of a community.
IMY's members, and especially its responsible members defined in section \ref{responsible_members}, shall be honest and transparent.
Brothers and sisters shall love one another, be cautious of wrongdoings, and forgive each other against all might.
Through fostering this community, IMY also has a responsibility for being keepers of \textbf{all} its neighbours and the salt of the Earth.

\section{Goal of the Constitution}
\label{constituition_goal}
The goal of this constitution is to structure this organisation
simply,
transparently,
unambiguously,
persistently,
and precisely.

\section{Crimes Against the Constitution}
\label{crimes}
Any deviations from the constitution can be voted to be a
\textbf{crime against the constitution}.
All crimes against the constitution are grounds for a re-election defined in section \ref{elections}.

\section{Constitution Storage}
\label{storage}
The constitution along with all logs defined in section \ref{log} shall be hosted on a public GitHub repository.
The constitution shall be written in at least British English and in \LaTeX with best practices.
This method of writing and public storage will ensure that the smallest changes made to the constitution, logs, or any other important public documents will be visible to all throughout its history.

\section{Changes to Constitution}
\label{changes}
There are
2
types of changes to the constitution:
\begin{enumerate}
      \item Content

            Any change that would change the meaning of the constitution shall be voted as defined in section
            \ref{elections}.
      \item Technical

            These changes are any changes that do not actually affect the meaning of the constitution.
            Examples of this type are changes to  the \LaTeX source code, spelling fixes, or minor grammatical corrections.
            They do not require an election to be merged.
\end{enumerate}

\subsection{Change Mechanism}
\label{change_mechanism}
All changes to the consitution shall be made as Pull Requests to the IMY GitHub from a forked repository.
\textbf{Anyone wishing to suggest any change to the constitution shall make a formal pull request along with a justification.}
A pull request containing content changes shall only be merged by voting results, defined in section \ref{elections}, as merge comments.
The secretary of the IMY defined in \ref{responsible_members} must hear informal change requests in Transparency Meetings defined in \ref{transparency_meetings}, and make the necessary change pull requests.

\section{Responsible Members}
\label{responsible_members}
Responsible members include distinct persons filling the below positions without term limits.
\begin{itemize}
      \item President

            The president is not to manage the other members; each of them act according to their own autonomy.
            The president is the \textbf{titular} liaison supervising IMY's contact with the Imam Mahdi Council.
      \item Secretary

            The secretary holds the maintenance of the constitution and any other secretarial tasks.
      \item Female \& Male Coordinators

            Both of these members coordinate events and programmes.
            There may be more than two coordinators, but at any point of time, one male, and one female must exist.

      \item Social Media Coordinators

            The social media coordinator shall, without exclusion, manage the social media of the IMY.
\end{itemize}

\section{Transparency Meetings}
\label{transparency_meetings}

The IMY shall be responsible to hold public \textbf{Transparency Meetings} every
6
weeks.
They shall happen in-person, but may happen remotely only under extraneous circumstances.
This event shall be advertised at least
3
days in advance.
The meetings may be postponed to meet scheduling needs, but may not be posted any longer than
2
weeks.

The secretary is responsible for scheduling and speaking neutrally at all transparency meetings.
\textbf{Their presence may not be substituted.}

The main goal of these meetings is to discuss plans, goals, and feedback from all IMY members.
Any transparency meeting can turn into an election as defined in section \ref{elections} by the demand of at least
3
persons present.

\textbf{The constituency meeting shall be followed by a group meal. }
This requires for all present to sit together and \textit{break bread}.

\section{Log}
\label{log}
The log keeps a record of all the transparency meetings' discussion and election results.
The secretary defined in section \ref{responsible_members} shall be responsible to take notes for these meetings as a log.
A transcription of these meetings is strictly unnecessary.
The log shall be made public as defined in section \ref{storage} within
24
hours of the transparency meeting.

\section{Elections}
\label{elections}
An election is a special transparency meeting.
An election meeting shall happen after every
8
constituency meetings as defined in section \ref{transparency_meetings}.
All voting occurs by least majority.
Any person present in the room may wish to vote or abstain.
Voting will happen by raising of the hand.

% \subsection{Required Elections}
\label{required_voting}
All changes to the constitution defined in section \ref{changes}
along with all changes to the responsible members defined in section \ref{responsible_members} shall happen by elections.
Changes to the constitution must be presented
1
Transparency Meeting defined in \ref{transparency_meetings}
before being voted in.

\section{Imam Mahdi Council}
\label{council}
The involvement of the council shall be managed and strictly prohibited to preserve the autonomy of the IMY, especially, but not exclusively, by the president defined in \ref{responsible_members}.
Finances from the council shall be strictly prohibited, or in the least discouraged; the IMY shall perform its own fundraising.


% \nocite{*}
% \printbibliography

\end{document}
